Now we describe modifications that we propose to original algorithm and intuition behind the proposals. We need to put on our \emph{Resource Adaptive Software System developer} hat on to understand this modifications.

(1) As the reduced adaptive program is a useful artifact that will be used in place of the original software, we hypothesize that it may not be drastically different then the original program. Reduction may incur many small local changes to software based on the relaxed specifications. As original HDD setups were designed to quickly converge to reduced input that is significantly \emph{smaller} then original input, they tend to make bigger chops earlier in the process. As changes to RASS are going to be local and smaller, we propose modification to original algorithm. Our algorithm always start with leaf nodes and it chops smallest possible unit at the beginning (statements for our tool). 

(2) Consider any two statement s1 and s2 existing at the same level in AST in the order s1,s2. Our algorithm always delete s2 before s1. Our deletions are always from right to left at same level in AST. (a) This prevents non compilable code and hence costly reverts, use will always be deleted before def. (b) Later read/write will be deleted before earlier read/write. Will this have better chance to keep program correct, for Alex to answer? Reverts will be needed only if any test in test suite failed.    

(3) Intuitively, changes for adaptations are going to be local somewhere at deeper depth level in program, we hypothesize that an early exit criterion is possible. We hypothesize that algorithm may not need to reach all the way to root node, It can stop much earlier. Accommodating the early exit possibility provides one more reason to start at leaf nodes first. Early exit criterion can be arbitrarily specified like 1/3rd of the depth of the tree or static or dynamic analysis or some feedback loop can be employed to define more accurate early exist criterion, if such criterion exists. our experiments validates such possibility.
